### 2015-06-25 abstract.tex
writing assignments

\noindent
Stuff
\vfill

>>>>

\noindent
Outline and writing assignments:
later the abstract will go here.
\begin{enumerate}
\item Introduction - Scott - Hasan - Gary - Jay 4 pages
   \begin{enumerate}
      \item resource drivers
      \item application drivers
      \item overall example which we will use for the test
      \item  need to answer the questions what we are doing, research  , prototype, aim, and what is new
   \end{enumerate}
\item Enabling Technologies - Jay - 1 page
   \begin{enumerate}
   	\item Sirocco
   	\item ADIOS
   	\item DataSpaces
   	\item Anything else
   \end{enumerate}
 \item {Proposed Research and Methods} - 14 pages
    \begin{enumerate}
       \item Application interface - Hasan, Manish, Gary, Kimmy, Jay, Mark
          \begin{enumerate}
            \item APIS - Hasan
            \item description of data - Gary
            \item collection of data reduction techniques - Mark
            \item data re-organization specification - Scott, Mark, Kimmy
            \item QoS - Hasan
            \item execution policies - Manish
            \item Initial placement and movement  - Gary
            \item policies - Jay
          \end{enumerate}
      \item Storage System - Jay, Carlos, Manish, Lee, Matthew, Feyi
      \begin{enumerate}
         \item migration - Lee
         \item resource management -Jay
         \item QoS - Carlos 
         \item Discovery - Jay
         \item Eviction metrics - Carlos
         \item Naming Service - Manish
         \item Estimation of Times - Feyi
      \end{enumerate}
    \end{enumerate}
\item Evaluation - 1 pages
\item Timetable of Activities - 1/2 page
\item Project Management Plan - 1 page
\item Project Objective  1/2 page
\end{enumerate}

\vfill
